\section{Conclusion and Future Work}

In this paper, we have presented a practical technique (and
its tool implementation, called \ourtool) for diagnosing
configuration errors in complex software systems.
Our experimental results show that \ourtool is effective in
diagnosing both crashing and non-crashing configuration errors
in realistic systems and do so with a
relatively small number of program profiles in the pre-built database.

The source code of \ourtool is publicly available at:
\url{http://config-errors.googlecode.com}.

\vspace{1mm}

%Besides general issues such as performance and ease of use,
Our future
work will focus on the following two topics:

\textbf{Fixing configuration errors.} After a configuration error
is localized, fixing it and verifying the patch is
often non-trivial and time-consuming. Thus, we
are interested in applying the current advance in
automated error-patching~\cite{PerkinsKLABCPSSSWZEP2009, rangefix} and
software self-adaptation~\cite{Wang:2009:STR, Mori:2011:LSU} techniques to
the problem of configuration error fixing.

%developing automated error-fixing techniques
%for general software misconfigurations.

\textbf{Improving configuration error reporting.} A high-quality
error report allows software users to understand and correct the problem
they encounter. 
Unfortunately, the quality of error reports often
decreases as software becomes more complex and configurable.
To address this problem, we plan to develop new error reporting mechanisms
to make configuration errors
more diagnosable.

%plan to investigate how to apply the current advance in
%program  retrofitting~\cite{} to the context of configuration management,
%and improve the error reporting mechanism in large, configurable software systems.

%Combined with automated configuration extraction. Our current
%technique requires developers to spend some one-time effort
%to encode a list of available configuration options. This step
%could be automated by combining with some exsiting work on
%automated configuration option extraction~\cite{}.

%Improve configuration problem reporting mechanism. Many
%programs would produce general error messages when configuration
%errors occur.


%$\blacksquare$ We demonstrate xxxx.
%Our technique can aid users in understanding and
%troubleshooting these errors xxx.
%oWe evaluate our work in detail

%We evaluate our work in detail on xxx.


%\vspace{1mm}

