We compared \ourtool with ConfAnalyzer, a heavyweight dynamic information
flow-based technique~\cite{Rabkin:2011:PPC}.
We chose ConfAnalyzer because it is one of the most recent and precise configuration
error diagnosis techniques. Also, its 
experimental data is publicly available.
ConfAnalyzer tracks the flow of labelled objects through the
program dynamically,
and treats a configuration option as a root cause if its
value may flow to a crashing point.
ConfAnalyzer works remarkably well for crashing errors, though as
described above these are often easy to diagnose even without tool
support. However, ConfAnalyzer cannot diagnose non-crashing errors.

The experimental results of ConfAnalyzer is shown in Figure~\ref{tab:results} (Column ``ConfAnalyzer'').
For the 9 crashing errors, \ourtool produced better results for 3 of them,
the same results for another 3, and worse results for the remaining 3.

ConfAnalyzer performs better on crashing errors
having shorter execution paths: an error exhibits
almost immediately after the software is launched.
In such cases, a small number of configuration options are initialized and
only few can flow to the crashing point. 
\ourtool fails to produce good diagnosis for these errors, because it can not identify
 the statistically-behavioral-deviated predicates based on the limited
program behaviors observed.

ConfAnalyzer outputs less accurate or no results
for errors (e.g., error 14 in Figure~\ref{tab:results}) where the root cause option value
flows into containers, or system calls. However, for those errors,
\ourtool can still reason about (to some extent) the \textit{consequence} of a misconfiguration
by the observed predicate behaviors, and even produce better diagnosis.



%Many cases only one configuration value flows into.
%For the classpath case, it misses. pollution?

%tracks them as
%they propagate during execution, and (3) identifies, for an
%observed failure, the subset of inputs that are potentially
%relevant for debugging that failure.

%\todo{Is ConfAnalyzer heavyweight?  If so, say so.}

