\begin{figure}[t]
\setlength{\tabcolsep}{.74\tabcolsep}
\small{
\begin{tabular}{|l|c|c||c|}
\hline
 Error ID. & \multicolumn{3}{|c|}{Rank of the Actual Root Cause} \\
  %& \multicolumn{3}{|c|}{Different Comparison Profile Selection Strategy} \\
\cline{2-4}
 Program & All Profiles& Random Selection&  Similarity-Based\\
 \hline
\hline
\multicolumn{4}{|l|}{Non-crashing errors}   \\
 \hline
 1. Randoop & 1 & 2 & 1\\
 2. Weka & 7 & 6 & 1\\
 3. JChord & 16 & 19 & 2\\
 4. Synoptic & 1 & 1 & 1\\
 5. Soot & 13 & 13 & 3\\
\hline
Average & 7.6 & 8.2 & 1.6 \\
\hline
\hline
\multicolumn{4}{|l|}{Crashing errors}   \\
\hline
 6. JChord & 1 & 1 &1\\
 7. JChord & 1 & 1 &1\\
 8. JChord & 17 & 17 &17\\
 9. JChord & 1 &  1&1\\
 10. JChord & 15 & 15 &15\\
 11. JChord & 16 & 16 &16\\
 12. JChord & 1 & 1 &1\\
 13. JChord & 25 & 25 &1\\
 14. JChord & 8 & 8 &8\\
\hline
Average & 9.4 & 9.4 & 6.7\\
\hline
\end{tabular}
}
\Caption{{\label{tab:selection} Comparison with different execution profile selection
strategies (Section~\ref{sec:choices}).
The last column ``Similarity-based'' is the selection strategy
used in \ourtool, and the data in that column is taken from Figure~\ref{tab:results}.}}
\end{figure}

We investigate the effects of:

\begin{itemize}
\item using traditional full slicing~\cite{Horwitz:1988} rather
than thin slicing~\cite{Sridharan:2007} in the Configuration
Propagation Analysis step (Section~\ref{sec:prop}) to compute the affected predicates.
Figure~\ref{tab:results}  (Column ``Full Slicing'') shows the results.
\item varying the comparison execution profiles from the pre-built database.
In particular, we compare the similarity-based selection strategy used in \ourtool
 (Section~\ref{sec:similar}) with two alternatives: selecting
all available profiles in the database, and
randomly selecting the same number of profiles as \ourtool used from the database.
Figure~\ref{tab:selection} shows the results.
\end{itemize}


$\blacksquare$ talk about the full slicing

We can see that varying the comparison strategy can result in
substantially different effects on the diagnosis results,
depending on the application being analyzed. Diagnosing
a non-crashing error is more sensitive in selecting similar
comparison execution profiles$\blacksquare$ than diagnosing
a crashing error.
For the \crash crashing errors, the only difference yielded
from using different profile selection strategies is on
the error 13. $\blacksquare$
