\section{Conclusion and Future Work}
\label{sec:conclusion}

Software evolution often causes software sytems to
exhibit undesired behaviors.
When they do, identifying the root causes
can be challenging, especially when a software's
behavior depends on a wide range of configuration options.

This paper describes \ourtool, a technique to help software
users to reconfigure a configurable software system. \ourtool
recommends configuration options whose values can be changed to
produce desired behavior on the new software version.
%\ourtool represents a novel synthesis of \todo{} steps:
%records \todo{} and collects \todo{}.
%\ourtool uses \todo{} to attribute .. to
%suspicious configuration options that should
%be re-setted. 
Our experimental results show that \ourtool
can accurately identify the root causes of
\errornum configuration problems in \subjnum real-world software systems.
The source code of \ourtool is publicly available
at: \url{http://config-errors.googlecode.com}.

We consider \ourtool as one step towards improving
the diagnosability of configurable software systems.
Our future work focuses on the following directions:

\vspace{-2mm}

\begin{itemize}
\item \textbf{User study.} We plan a user study to evaluate
\ourtool's usefulness to end-users. A challenge
will be finding study participants who are familiar
with our subject programs.

\item \textbf{Formulating guidance of error diagnosis.}
An important question that is not answered in \ourtool
is that how to automatically distinguish software bugs from 
configuration errors, when a software system exhibits
some undesired behavior. We plan to formulate guidance
regarding when the user should give up on \ourtool
and assume the error is not related to a configuration option.

\item \textbf{Improving configuration error reporting and fixing.}
A bug report of a configuration error must combine the
failing software state with its use scenario.
When fixing a configuration error, there is no obviously ``correct'' way to
build configuration logic. In addition, unlike fixing a bug once,
every software user has to be informed on the right way to
configure the system.  Perhaps as a result, misconfigurations
have been one of the dominant causes of system issues and
is likely to continue so. To address these related problems,
we plan to explore the existing software configuration errors
to summarize error patterns, and then use machine learning
techniques to synthesize good-quality error reports and fixes.

%; \todo{evolve} the end-user should imbibe the
%knowledge and manage cross-version configurations.


\end{itemize}

%As future work,  We are also interested
%in developing new problem reporting mechanisms to
%make configuration problems more diagnosable.
%Yet another direction of work will be studying
%test-suite augmentation techniques to automatically
%create new tests that can reveal potential configuration
%problems, as software evolves.
